Hydra Battles and Cie

### 2021-09-01 doc/part-hydras.tex
revision chapter 4 (up to page 91)

\label{alpha0-def}
For instance, the ordinal  $\omega^\omega+\omega^3\times 5+2$ is represented by the following term:

@@

Equality in \texttt{E0} is just Leibniz equality. Note that, since \texttt{nf} is
defined by a Boolean function, for  any term $\alpha:\texttt{T1}$, there exists at most one proof of \texttt{nf $\alpha$}, thus two ordinals of type \texttt{E0} are
equal if and only iff their projection to \texttt{T1} are equal (see also Sect.~\vref{sect:eq-proof-unicity}).

@@

\input{movies/snippets/E0/nfProofUnicity}

\input{movies/snippets/E0/E0EqIff}

@@

@@

\input{movies/snippets/T1/succIsPlusOne}

@@

\input{movies/snippets/T1/transfiniteRecursor}

The following tactic starts a proof by  transfinite induction on any ordinal \mathcolor{$\alpha<\epsilon_0$}.

\input{movies/snippets/T1/transfiniteInduction}

@@

We build an instance of \texttt{ON}, and prove its correction w.r.t. Schutte's model.

@@

    In Module   \href{https://github.com/coq-community/hydra-battles/blob/master/theories/ordinals/OrdinalNotations/OmegaOmega.v}{theories/ordinals/OrdinalNotations/OmegaOmega.v},
    we represent ordinals below $\omega^\omega$ by list of pairs of natural numbers (with the same coefficient shift as in \texttt{T1}).
    For instance, the ordinal $\omega^4\times 10 + \omega^3 + \omega+ 5$ is represented by the list \texttt{(4,9)::(3,0)::(1,0)::(0,4)::nil}.

@@

@@

>>>>

\label{alpha0-def}
For instance, the ordinal  $\omega^\omega+\omega^3\times 5+2$ is represented by the following term of type \texttt{T1}:

@@

Equality in \texttt{E0} is just Leibniz equality. Note that, since \texttt{nf} is
defined by a Boolean function, for  any term $\alpha:\texttt{T1}$, there exists at most one proof of \texttt{nf $\alpha$}, thus two ordinals of type \texttt{E0} are
equal if and only if their projection to \texttt{T1} are equal (see also Sect.~\vref{sect:eq-proof-unicity}).

@@

\inputsnippets{E0/nfProofUnicity}
\inputsnippets{E0/E0EqIff}

@@

The function \texttt{succ} on \texttt{T1} is extended to \texttt{E0} the following way:

 \inputsnippets{E0/SuccOnE0}

@@

\inputsnippets{T1/succIsPlusOne, T1/succIsPlusOnez}

@@

Traditionnally, well-founded induction on ordinals is called \emph{transfinite induction}.

\inputsnippets{T1/transfiniteRecursor, T1/transfiniteInduction}

As a corollary, the order \texttt{Lt} on type \texttt{Ord} is well-founded too.

\inputsnippets{E0/E0LtWf}.

@@

We build an instance of \texttt{ON}, and prove its correctness w.r.t. Schutte's model.

@@

    In Module   \href{https://github.com/coq-community/hydra-battles/blob/master/theories/ordinals/OrdinalNotations/OmegaOmega.v}{theories/ordinals/OrdinalNotations/OmegaOmega.v},
    we represent ordinals below $\omega^\omega$ by lists of pairs of natural numbers (with the same coefficient shift as in \texttt{T1}).
    For instance, the ordinal $\omega^4\times 10 + \omega^3 + \omega+ 5$ is represented by the list \texttt{(4,9)::(3,0)::(1,0)::(0,4)::nil}.

\inputsnippets{OmegaOmega/LODef}

@@

  \inputsnippets{OmegaOmega/succPlusMult}

@@

    \inputsnippets{OmegaOmega/refineDef, OmegaOmega/phi0Ref,
      OmegaOmega/succRef, OmegaOmega/plusRef,
      OmegaOmega/multRef}

    In order to make an ordinal notation for $\omega^\omega$, we follow the same steps as for $\epsilon_0$:
    \begin{enumerate}
    \item Define an order \texttt{lt}, which refines the order
      \texttt{lt} on \texttt{T1}.
      \inputsnippets{OmegaOmega/compareDef}
      \inputsnippets{ OmegaOmega/ltDef, OmegaOmega/ltRef}

    \item Define the predicate ``to be in normal form''.
      \inputsnippets{OmegaOmega/nfDef}
    \item Define a class \texttt{OO} of terms in normal form, and an embedding from \texttt{E0} into \texttt{OO}.
      \inputsnippets{OmegaOmega/OODef}
       \inputsnippets{OmegaOmega/embedDef}
      \item Infer well-foundedness of the order on \texttt{OO}.
    \inputsnippets{OmegaOmega/ltWf}

    \inputsnippets{OmegaOmega/ONOO, OmegaOmega/OOz}

    Let us show a few examples.

    \inputsnippets{OmegaOmega/OODemo}
